Whittaker Models for Real Groups

### 2024-04-01 whittaker.tex
Further small typos

 Recall $Q_{\theta}(\R)=\Gad^{\theta_{\ad}}/\Kad$. By definition $\Gad^{\theta_{\ad}}$ is contained in the normalizer $\mathrm{Norm}_G(K)$; therefore it acts on~$(\g, K)$-modules. Any element of~$\Kad$ takes a $(\g,K)$-module to an equivalent one, therefore $Q_{\theta}(\R)$ acts on~$(\g, K)$-module. This preserves the property of being a discrete series, and of being large. Furthermore, by \cite[Lemma 6.18 and Remark 6.19]{Contragredient} the action preserves $L$-packets. Therefore $Q_{\theta}(\R)$ acts transitively on the large representations in a discrete series $L$-packet.

>>>>

 Recall $Q_{\theta}(\R)=\Gad^{\theta_{\ad}}/\Kad$. By definition $\Gad^{\theta_{\ad}}$ is contained in the normalizer $\mathrm{Norm}_G(K)$; this determines a canonical action of $\Gad^{\theta_{\ad}}$ on~$(\g, K)$-modules.
 Any element of~$\Kad$ takes a $(\g,K)$-module to an equivalent one, and this gives an action of $Q_{\theta}(\R)$ on equivalence classes of irreducible $(\g, K)$-modules.
 This preserves the property of being a discrete series, and of being large.
 Furthermore, by \cite[Lemma 6.18 and Remark 6.19]{Contragredient} the action preserves $L$-packets.
 Therefore $Q_{\theta}(\R)$ acts transitively on the large representations in a discrete series $L$-packet.
